---
title: ""
author: "Comparative Use of Hydrologic Indicators to Determine the Effects of Flow Regimes on Water Quality in Three Channels across Southern Florida, USA"
date: "8/29/2021"
output: html_document
---

```
###Three channels include: Shark River Slough, Peace River and Hillsboro Canal####
##############Shark River Slough######################################
```{r}
library(dbhydroR)
library(dplyr)
library(lubridate)
library(ggplot2)
library(segmented)
#get and name water quality file 
Srs3_TP = read.csv("SRS3-TP_mgl.csv", header =T)
head(Srs3_TP)

Remove NA rows
Srs3_TP = na.omit(Srs3_TP)
attach(Srs3_TP)


TP_F1= Srs3_TP
#convert flow/discharge from cfs to cms
TP_F1= mutate(TP_F1,
  Discharge = Flow*0.0283 ,
)
head(TP_F1)

TP_F1= mutate(TP_F1,
  Q6 = log10(Discharge) ,
  C6 = log10(TP)
  
)
#remove the negative and zero rows
TP_F1 = na.omit(TP_F1)
head(TP_F1)
attach(TP_F1)

TPplot <- ggplot(TP_F1, aes(x= Q6, y= C6))+geom_point()
TPplot
# linear model
#linearModelVar <- lm(loggedtemp ~ loggeddischarge, datavar)
linearModelVar6 <- lm(C6 ~ Q6, TP_F1)
#display linear model
linearModelVar6
summary(linearModelVar6)

# Davies test for significant breakpoint in the slope
TPdavies <- davies.test(linearModelVar6,seg.Z =~Q6,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
TPdavies 
#########################
#segmented linear relationship model
TP.seg <- segmented(linearModelVar6, seg.Z = ~ Q6,it.max=1000)
#summary(tp.seg1)
summary.seg6 = summary(TP.seg)
summary.seg6

#estimate bp which is already in the summary
TP.seg$psi

TPestbp <-summary.segmented(TP.seg)$psi [1,2]
TPestbp

TPestderror <- summary.segmented(TP.seg)$psi [1,3]
slope(TP.seg)
#confidence interval

confint(TP.seg, 'Q6', level=0.95, rev.sgn=FALSE, var.diff=FALSE,
        digits=max(4, getOption("digits") - 1))


my.fitted6 <- fitted(TP.seg)
#my.model <- data.frame(discharge=datavar$loggeddischarge, loggedturbidity=my.fitted)
my.model6 <- data.frame(Discharge=TP_F1$Q6, C6=my.fitted6)

high.TP= subset(TP_F1, Q6 >= TP.seg$psi[2])
low.TP <- subset(TP_F1,Q6 < TP.seg$psi[2])

#anova

TPlowaov1 <-aov(low.TP$C6 ~ low.TP$Q6, data = low.TP)
summary(TPlowaov1)

TPhighaov1 <-aov(high.TP$C6 ~ high.TP$Q6, data = high.TP)
summary(TPhighaov1)

TPplot <- ggplot(TP_F1,aes(x=Q6, y= C6))+
  geom_point( aes( x=Q6, y= C6), color= 'black') #shape = temppch)
TPplot


ggplot(my.model6, aes(x=Q6, y=C6)) + geom_line()
breakpointplot6=TPplot + geom_line(data = my.model6, aes(x = Q6, y = C6), colour = "red", size = 1.25)

TPmy.lines <- TP.seg$psi[, 2]
#create tiff file
#tiff("blahTPplot1.tiff", width = 5, height =3, units = 'in', res = 600)
TPplot1 <- breakpointplot6+geom_vline(xintercept=TPmy.lines,linetype="dashed", col ="red", size= 1)+
xlab(expression(Discharge~(m^3~s^-1)))+ylab(expression(TP~(µmol~L^-1)))+
  theme(panel.border =  element_rect(color = "black", fill = NA, size= 1),
        panel.background=element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position="top")+
  theme(axis.text.x = element_text(color = "grey20", size = 12,  hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12,  hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 16,  hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 16,  hjust = .5, vjust = .5, face = "plain"))+
  #transfomrm scale  back to normal and round to two decimal places
  scale_x_continuous(breaks = c(-2, -1, 0, 1,2,3), labels =round(c(10^(-2),10^(-1), 10^(0),10^(1),10^(2),10^(3)), 3))+
    scale_y_continuous(breaks =c(-1, -0.5, 0, 0.5, 1, 1.25), labels =round(c(10^(-1),10^(-0.5), 10^(0), 10^(0.5),10^(1),10^(1.25)),1))
      #breaks=seq(0,100, by = 20)))
  #text(x, y, labels)
TPplot1  

####################################################
#select nitrate-nitrite
Srs3_NN = read.csv("srs3_nn_f_new_mg_L_final_for_plot.csv", header = T)

attach(Srs3_NN)
head(Srs3_NN)

Srs3_NN= mutate(Srs3_NN,
  Discharge = Flow*0.0283 ,
)

head(Srs3_NN)
NN_F = Srs3_NN 

NN_F= mutate(PR_T_F,
  TP = TP*0.031,
  C= log10(TP)
  )

NN_F= mutate(NN_F,
  Q1 = log10(Discharge) ,
  C1 = log10(NN)
  
)

NN_F = na.omit(NN_F)
head(NN_F)
attach(NN_F)

#nnplot <- ggplot(datavar, aes(x=loggeddischarge, y= loggedtemp))+geom_point()
nnplot <- ggplot(NN_F, aes(x= Q1, y= C1))+geom_point()
nnplot
# linear model
#linearModelVar <- lm(loggedtemp ~ loggeddischarge, datavar)
linearModelVar <- lm(C1 ~ Q1, NN_F)
#display linear model
summary(linearModelVar)

# Davies test for significant breakpoint
#turbdavies <- davies.test(linearModelVar,seg.Z =~loggeddischarge,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
nndavies <- davies.test(linearModelVar,seg.Z =~Q1,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
nndavies 
#########################

pscore.test(linearModelVar, k = 10, alternative = c("two.sided", "less", "greater"),
            values=NULL, dispersion=NULL, df.t=NULL, more.break=FALSE)

nn.seg <- segmented(linearModelVar, seg.Z = ~ Q1,it.max=1000)
#summary(tp.seg1)
summary.seg1 = summary(nn.seg)
summary.seg1

nn.seg$psi
#estimate bp which is already in the summary
nnestbp <-summary.segmented(nn.seg)$psi [1,2]
nnestbp

nnestderror <- summary.segmented(nn.seg)$psi [1,3]
slope(nn.seg)

confint(nn.seg, 'Q1', level=0.95, rev.sgn=FALSE, var.diff=FALSE,
        digits=max(4, getOption("digits") - 1))


my.fitted1 <- fitted(nn.seg)
#my.model <- data.frame(discharge=datavar$loggeddischarge, loggedturbidity=my.fitted)
my.model1 <- data.frame(Discharge=NN_F$Q1, C1=my.fitted1)

high.nn= subset(NN_F, Q1 >= nn.seg$psi[2])
low.nn <- subset(NN_F,Q1 < nn.seg$psi[2])

#anova

nnlowaov1 <-aov(low.nn$C1 ~ low.nn$Q1, data = low.nn)
summary(nnlowaov1)

nnhighaov1 <-aov(high.nn$C1 ~ high.nn$Q1, data = high.nn)
summary(nnhighaov1)

nnplot <- ggplot(NN_F,aes(Station, x=Q1, y= C1))+
  geom_point( aes( x=Q1, y= C1), color= 'black') #shape = temppch)
nnplot


ggplot(my.model1, aes(x=Q1, y=C1)) + geom_line()
breakpointplot1=nnplot + geom_line(data = my.model1, aes(x = Q1, y = C1), colour = "red", size = 1.25)

nnmy.lines <- nn.seg$psi[, 2]


tiff("NNfinalplot1_manuscipt.tiff", width = 5, height =3, units = 'in', res = 600)
nnplot1 <- breakpointplot1+geom_vline(xintercept=nnmy.lines,linetype="dashed", col ="red", size= 1)+
  #xlab(expression(Discharge~(m^3~s^-1)))+ylab(expression(NO[3]~(mg~L^-1)))+
  xlab(expression(Discharge~(m^3~s^-1)))+ylab(expression(NN~(mg~L^-1)))+
  theme(panel.border =  element_rect(color = "black", fill = NA, size=1),
        panel.background=element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position="top")+
  theme(axis.text.x = element_text(color = "grey20", size = 11,  hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 11,  hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 11,  hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 11,  hjust = .5, vjust = .5, face = "plain"))+
        #axis.text.x     = element_text(size = 8)
  #transfomrm scale  back to normal and round to two decimal places
  scale_x_continuous(breaks = c(-2, -1, 0, 1,2,3), labels =round(c(10^(-2),10^(-1), 10^(0),10^(1),10^(2),10^(3)), 3))+
    scale_y_continuous(breaks = c(-3,-2, -1.0,  0.0, 1), labels =round(c(10^(-3), 10^(-2), 10^(-1.0), 10^(0.0), 10^(1.0)),3))
    
  #scale_y_continuous(breaks = c(0, 1, 1.5, 2), labels =round(c(10^(0), 10^(1), 10^(1.5), 10^(2)),2))                    
nnplot1

library(dbhydroR)
Srs3_SpC= get_hydro(dbkey = "89870",
         date_min = "2004-01-01", date_max = "2018-12-31")
#write.csv(Srs3_SpC, file = "srs3_short_SpC.csv", row.names =F)
Srs3_flow= get_hydro(dbkey = "89858",
         date_min = "2004-01-01", date_max = "2018-12-31")
attach(Srs3_flow)
#write.csv(Srs3_flow, file = "srs3_short_flow.csv", row.names =F)

#write.csv(S31_flow, file = "S31_flow_cleaned.csv",row.names =F)
#attach(Srs3_SpC)
head(Srs3_SpC)
head(Srs3_flow)

Srs3_flow = na.omit(Srs3_flow)

attach(Srs3_flow)

Srs3_SpC = na.omit(Srs3_SpC)
attach(Srs3_SpC)

Srs3_comb_SpC = merge(Srs3_flow, Srs3_SpC, by ="date")


#MR_Con= rename(MR_Con, Specific_Conductivity_umhos_cm = RESULT)
Srs3_comb_SpC= rename(Srs3_comb_SpC, SpC = "022908295_SCOND_uS/cm" )
Srs3_comb_SpC= rename(Srs3_comb_SpC,Flow = '022908295_FLOW_cfs')
#Srs3_comb_SpC
#add more columns based on exisiting columns
write.csv(Srs3_comb_SpC, file = "Srs3_comb_SpC.csv",row.names =F)

 SpC_F =read.csv("Srs3_comb_SpC.csv", header =T)
attach (SpC_F)
head(SpC_F)

SpC_F= mutate(SpC_F,
  Discharge = Flow*0.0283 ,
  
)
head(SpC_F)

SpC_F= mutate(SpC_F,
  Q9 = log10(Discharge) ,
  C9 = log10(SpC)
  
)

SpC_F = na.omit(SpC_F)
SpC_F <- SpC_F[SpC_F$SpC > 0, ]
SpC_F <- SpC_F[SpC_F$Discharge > 0, ]
#Srs3_comb_Temp <- Srs3_comb_Temp[Srs3_comb_Temp$Flow > 0, ]

head(SpC_F)
attach(SpC_F)
#write.csv(SpC_F, file = "SpC_F.csv",row.names =F)

SpCplot <- ggplot(SpC_F, aes(x= Q9, y= C9))+geom_point()
SpCplot
# linear model
#linearModelVar <- lm(loggedtemp ~ loggeddischarge, datavar)
linearModelVar9 <- lm(C9 ~ Q9, SpC_F)
#display linear model
linearModelVar9
summary(linearModelVar9)
# Davies test for significant breakpoint
#turbdavies <- davies.test(linearModelVar,seg.Z =~loggeddischarge,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
SpCdavies <- davies.test(linearModelVar9,seg.Z =~Q9,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
SpCdavies 
#########################

pscore.test(linearModelVar9, k = 10, alternative = c("two.sided", "less", "greater"),
            values=NULL, dispersion=NULL, df.t=NULL, more.break=FALSE)

SpC.seg <- segmented(linearModelVar9, seg.Z = ~ Q9,it.max=1000)
#summary(SpC.seg1)
summary.seg9= summary(SpC.seg)
summary.seg9

SpC.seg$psi
#estimate bp which is already in the summary
SpCestbp <-summary.segmented(SpC.seg)$psi [1,2]
SpCestbp

SpCestderror <- summary.segmented(SpC.seg)$psi [1,3]
slope(SpC.seg)

confint(SpC.seg, 'Q9', level=0.95, rev.sgn=FALSE, var.diff=FALSE,
        digits=max(4, getOption("digits") - 1))


my.fitted9 <- fitted(SpC.seg)
#my.model <- data.frame(discharge=datavar$loggeddischarge, loggedturbidity=my.fitted)
my.model9 <- data.frame(Discharge=SpC_F$Q9, C9=my.fitted9)

high.SpC= subset(SpC_F, Q9 >= SpC.seg$psi[2])
low.SpC <- subset(SpC_F,Q9 < SpC.seg$psi[2])

#anova

SpClowaov1 <-aov(low.SpC$C9 ~ low.SpC$Q9, data = low.SpC)
summary(SpClowaov1)

SpChighaov1 <-aov(high.SpC$C9 ~ high.SpC$Q9, data = high.SpC)
summary(SpChighaov1)

SpCplot <- ggplot(SpC_F,aes(x=Q9, y= C9))+
  geom_point( aes( x=Q9, y= C9), color= 'black') #shape = temppch)
SpCplot


ggplot(my.model9, aes(x=Q9, y=C9)) + geom_line()
breakpoint9=SpCplot + geom_line(data = my.model9, aes(x = Q9, y = C9), colour = "red", size = 1.25)

SpCmy.lines <- SpC.seg$psi[, 2]
tiff("S_review_SpCplot1.tiff", width = 5, height =3, units = 'in', res = 600)
SpCplot1 <- breakpoint9+geom_vline(xintercept=SpCmy.lines,linetype="dashed", col ="red", size= 1)+
  xlab(expression(Discharge~(m^3~s^-1)))+ylab(expression(SC~(uS~cm^-1)))+
  theme(panel.border =  element_rect(color = "black", fill = NA, size=1),
        panel.background=element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position="top")+
  theme(axis.text.x = element_text(color = "grey20", size = 11,  hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 11,  hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 11,  hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 11,  hjust = .5, vjust = .5, face = "plain"))+
  #transfomrm scale  back to normal and round to two decimal places
  scale_x_continuous(breaks = c(-3,-2, -1, 0), labels =round(c(10^(-3),10^(-2), 10^(-1), 10^(0)),3))+
    scale_y_continuous(breaks = c(2,3, 4, 5), labels =round(c(10^(2),10^(3),10^(4),10^(5)),))
                      
SpCplot1

######################## Peace River################################
NN_F = read.csv("prb_NN_F_final_noflag_no_dup.csv", header =T)
attach(NN_F)
NN_F = na.omit(NN_F)

head(NN_F)

#to convert from factor to date gonthough Posixit 
#NN_F$Date<-strptime(Date,format="%m/%d/%Y") #defining what is the original format of your date
#NN_F$Date<-as.Date(NN_F$Date,format="%m-%d-%Y") #defining what is the desired format of your date


# subset POR for NN 2004 to 2018 daily average discharge
#NN_F <- NN_F %>%
        #filter(Date >= as.Date('2004-01-01') & Date <= as.Date('2018-12-31'))
#attach(NN_F)


#NNplot <- ggplot(datavar, aes(x=loggeddischarge, y= loggedtemp))+geom_point()
NNplot <- ggplot(NN_F, aes(x= Q1, y= C1))+geom_point()
NNplot
# linear model
#linearModelVar <- lm(loggedtemp ~ loggeddischarge, datavar)

linearModelVar1 <- lm(C1 ~ Q1, NN_F)
#display linear model
summary(linearModelVar1)

# Davies test for significant breakpoint
#turbdavies <- davies.test(linearModelVar,seg.Z =~loggeddischarge,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
NNdavies <- davies.test(linearModelVar1,seg.Z =~Q1,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
NNdavies 
#########################

pscore.test(linearModelVar1, k = 10, alternative = c("two.sided", "less", "greater"),
            values=NULL, dispersion=NULL, df.t=NULL, more.break=FALSE)

nn.seg1 <- segmented(linearModelVar1, seg.Z = ~ Q1,it.max=1000)
#summary(tp.seg1)
summary.seg.nn = summary(nn.seg1)
summary.seg.nn

confint(nn.seg1, 'Q1', level=0.95, rev.sgn=FALSE, var.diff=FALSE,
        digits=max(4, getOption("digits") - 1))
nn.seg1$psi
#estimate bp which is already in the summary
nnestbp1 <-summary.segmented(nn.seg1)$psi [1,2]
nnestbp1

nnestderror1 <- summary.segmented(nn.seg1)$psi [1,3]
slope(nn.seg1)


my.fitted2 <- fitted(nn.seg1)
#my.model <- data.frame(discharge=datavar$loggeddischarge, loggedturbidity=my.fitted)
my.model2 <- data.frame(Discharge=NN_F$Q1, C1=my.fitted2)

high.nn= subset(NN_F, Q1 >= nn.seg1$psi[2])
low.nn <- subset(NN_F,Q1 < nn.seg1$psi[2])

#anova

nnlowaov <-aov(low.nn$C1 ~ low.nn$Q1, data = low.nn)
summary(nnlowaov)

nnhighaov <-aov(high.nn$C1 ~ high.nn$Q1, data = high.nn)
summary(nnhighaov)

NNplot <- ggplot(NN_F,aes(Station, x=Q1, y= C1))+
  geom_point(aes( x=Q1, y= C1), color= 'black') #shape = temppch)
NNplot


ggplot(my.model2, aes(x=Q1, y=C1)) + geom_line()
breakpointplot2=NNplot + geom_line(data = my.model2, aes(x = Q1, y = C1), colour = "red", size = 1.25)

nnmy.lines <- nn.seg1$psi[, 2]



tiff("review_NNlot1_manuscript.tiff", width = 5, height =3, units = 'in', res = 600)
nnplot1 <- breakpointplot2+geom_vline(xintercept=nnmy.lines,linetype="dashed", col ="red", size= 1)+
  xlab(expression(Discharge~(m^3~s^-1)))+ylab(expression(NN~(mg~L^-1)))+
  theme(panel.border =  element_rect(color = "black", fill = NA, size=1),
        panel.background=element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position="top")+
  theme(axis.text.x = element_text(color = "grey20", size = 12,  hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12,  hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 16,  hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 16,  hjust = .5, vjust = .5, face = "plain"))+
        #axis.text.x     = element_text(size = 8)
  #transfomrm scale  back to normal and round to two decimal places
  scale_x_continuous(breaks = c(-2, -1, 0, 1,2,3), labels =round(c(10^(-2),10^(-1), 10^(0),10^(1),10^(2),10^(3)), 3))+
    scale_y_discrete(limits = c(-2, -1, 0,1), labels =round(c(10^(-2), 10^(-1),10^(0), 10^(1)),3))
  #scale_y_discrete(limits = c(-2, -1.25, -0.5), labels =round(c(10^(-2), 10^(-1.25), 10^(-0.5)),2))  
  #scale_y_continuous(breaks = c(0, 1, 1.5, 2), labels =round(c(10^(0), 10^(1), 10^(1.5), 10^(2)),2))                    
nnplot1
dev.off()
t1 = (mean(Discharge)/mean(NN))* (sd(NN)/sd(Discharge))
 
#t = CVc/CVq
t1
############################
Cl_F = read.csv('prb_cl_f_short.csv', header =T)

attach(Cl_F)
Cl_F = na.omit(Cl_F)

Cl_F$Date<-strptime(Date,format="%m/%d/%Y") #defining what is the original format of your date
Cl_F$Date<-as.Date(Cl_F$Date,format="%m-%d-%Y") #d


Cl_F <- Cl_F %>%
        filter(Date >= as.Date('2004-01-01') & Date <= as.Date('2018-12-31'))
head(Cl_F)
attach(Cl_F)
#Clplot <- ggplot(datavar, aes(x=loggeddischarge, y= loggedtemp))+geom_point()
Clplot <- ggplot(Cl_F, aes(x= Q3, y= C3))+geom_point()
Clplot
# linear model
#linearModelVar <- lm(loggedtemp ~ loggeddischarge, datavar)
linearModelVar3 <- lm(C3 ~ Q3, Cl_F)
#display linear model
summary(linearModelVar3)

# Davies test for significant breakpoint
#turbdavies <- davies.test(linearModelVar,seg.Z =~loggeddischarge,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
cldavies <- davies.test(linearModelVar3,seg.Z =~Q3,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
cldavies 
#########################

pscore.test(linearModelVar3, k = 10, alternative = c("two.sided", "less", "greater"),
            values=NULL, dispersion=NULL, df.t=NULL, more.break=FALSE)

cl.seg <- segmented(linearModelVar3, seg.Z = ~ Q3,it.max=1000)
#summary(tp.seg1)
summary.seg3 = summary(cl.seg)
summary.seg3

confint(cl.seg , 'Q3', level=0.95, rev.sgn=FALSE, var.diff=FALSE,
        digits=max(4, getOption("digits") - 1))
cl.seg$psi
#estimate bp which is already in the summary
clestbp <-summary.segmented(cl.seg)$psi [1,2]
clestbp

clestderror <- summary.segmented(cl.seg)$psi [1,3]
slope(cl.seg)



my.fitted3 <- fitted(cl.seg)
#my.model <- data.frame(discharge=datavar$loggeddischarge, loggedturbidity=my.fitted)
my.model3 <- data.frame(Discharge=Cl_F$Q3, C3=my.fitted3)

high.cl= subset(Cl_F, Q3 >= cl.seg$psi[2])
low.cl <- subset(Cl_F,Q3 < cl.seg$psi[2])

#anova

cllowaov1 <-aov(low.cl$C3 ~ low.cl$Q3, data = low.cl)
summary(cllowaov1)

clhighaov1 <-aov(high.cl$C3 ~ high.cl$Q3, data = high.cl)
summary(clhighaov1)

Clplot <- ggplot(Cl_F,aes(Station, x=Q3, y= C3))+
  geom_point( aes( x=Q3, y= C3), color= 'black') #shape = temppch)
Clplot



ggplot(my.model3, aes(x=Q3, y=C3)) + geom_line()
breakpointplot3=Clplot + geom_line(data = my.model3, aes(x = Q3, y = C3), colour = "red", size = 1.25)

clmy.lines <- cl.seg$psi[, 2]

tiff("review_Clplot3.tiff", width = 5, height =4, units = 'in', res = 600)
Clplot1 <- breakpointplot3+geom_vline(xintercept=clmy.lines,linetype="dashed", col ="red", size= 1)+
  xlab(expression(Discharge~(m^3~s^-1)))+ylab(expression(Cl~(mg~L^-1)))+
  theme(panel.border =  element_rect(color = "black", fill = NA, size=1),
        panel.background=element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position="top")+
  theme(axis.text.x = element_text(color = "grey20", size = 12,  hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12,  hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 16,  hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 16,  hjust = .5, vjust = .5, face = "plain"))+
        #axis.text.x     = element_text(size = 8)
  #transfomrm scale  back to normal and round to two decimal places
  scale_x_continuous(breaks = c(-1, 0, 1,2,3), labels =round(c(10^(-1), 10^(0), 10^(1), 10^(2), 10^(3)),2))+
    scale_y_discrete(limits = c(1,2), labels =round(c( 10^(1), 10^(2))))
  #scale_y_continuous(breaks = c(0, 1, 1.5, 2), labels =round(c(10^(0), 10^(1), 10^(1.5), 10^(2)),2))                    
Clplot1
dev.off()

 
#t = CVc/CVq
t3

#############################################################
tss_F = read.csv('prb_tss_f_short.csv', header =T)

attach(tss_F)
tss_F = na.omit(tss_F)

tss_F$Date<-strptime(Date,format="%m/%d/%Y") #defining what is the original format of your date
tss_F$Date<-as.Date(tss_F$Date,format="%m-%d-%Y") #d


tss_F <- tss_F %>%
        filter(Date >= as.Date('2004-01-01') & Date <= as.Date('2018-12-31'))
attach(tss_F)
head(tss_F)
#duplicated(tss_F)
#which(duplicated(tss_F))

#tssplot <- ggplot(datavar, aes(x=loggeddischarge, y= loggedtemp))+geom_point()
tssplot <- ggplot(tss_F, aes(x= Q4, y= C4))+geom_point()
tssplot
# linear model
#linearModelVar <- lm(loggedtemp ~ loggeddischarge, datavar)
linearModelVar4 <- lm(C4 ~ Q4, tss_F)
#display linear model
linearModelVar4
summary(linearModelVar4)
# Davies test for significant breakpoint
#turbdavies <- davies.test(linearModelVar,seg.Z =~loggeddischarge,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
tssdavies <- davies.test(linearModelVar4,seg.Z =~Q4,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
tssdavies 
#########################

pscore.test(linearModelVar4, k = 10, alternative = c("two.sided", "less", "greater"),
            values=NULL, dispersion=NULL, df.t=NULL, more.break=FALSE)

tss.seg <- segmented(linearModelVar4, seg.Z = ~ Q4,it.max=1000)
#summary(tp.seg1)
summary.seg3 = summary(tss.seg)
summary.seg3

confint(tss.seg , 'Q4', level=0.95, rev.sgn=FALSE, var.diff=FALSE,
        digits=max(4, getOption("digits") - 1))
tss.seg$psi
#estimate bp which is already in the summary
tssestbp <-summary.segmented(tss.seg)$psi [1,2]
tssestbp

tssestderror <- summary.segmented(tss.seg)$psi [1,3]
slope(tss.seg)



my.fitted4 <- fitted(tss.seg)
#my.model <- data.frame(discharge=datavar$loggeddischarge, loggedturbidity=my.fitted)
my.model4 <- data.frame(Discharge=tss_F$Q4, C4=my.fitted4)

high.tss= subset(tss_F, Q4 >= tss.seg$psi[2])
low.tss <- subset(tss_F,Q4 < tss.seg$psi[2])

#anova

tsslowaov1 <-aov(low.tss$C4 ~ low.tss$Q4, data = low.tss)
summary(tsslowaov1)

tsshighaov1 <-aov(high.tss$C4 ~ high.tss$Q4, data = high.tss)
summary(tsshighaov1)

tssplot <- ggplot(tss_F,aes(x=Q4, y= C4))+
  geom_point( aes( x=Q4, y= C4), color= 'black') #shape = temppch)
tssplot


ggplot(my.model4, aes(x=Q4, y=C4)) + geom_line()
breakpointplot4=tssplot + geom_line(data = my.model4, aes(x = Q4, y = C4), colour = "red", size = 1.25)

tssmy.lines <- tss.seg$psi[, 2]
tiff("review_TSSplot1.tiff", width = 5, height =3, units = 'in', res = 600)
tssplot1 <- breakpointplot4+geom_vline(xintercept=tssmy.lines,linetype="dashed", col ="red", size= 1)+
  xlab(expression(Discharge~(m^3~s^-1)))+ylab(expression(TSS~(mg~L^-1)))+
  theme(panel.border =  element_rect(color = "black", fill = NA, size=1),
        panel.background=element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position="top")+
  theme(axis.text.x = element_text(color = "grey20", size = 12,  hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12,  hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 16,  hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 16,  hjust = .5, vjust = .5, face = "plain"))+
        #axis.text.x     = element_text(size = 8)
  #transfomrm scale  back to normal and round to two decimal places
  scale_x_continuous(breaks = c(-1, 0, 1,2,3), labels =round(c(10^(-1), 10^(0), 10^(1), 10^(2), 10^(3)),2))+
    scale_y_discrete(limits= c(0,1, 2), labels =round(c(10^(0), 10^(1), 10^(2))))
  #scale_y_continuous(breaks = c(0, 1, 1.5, 2), labels =round(c(10^(0), 10^(1), 10^(1.5), 10^(2)),2))                    
tssplot1
dev.off()

######################################################
```{r}
TP_F = read.csv('prb_TP_F2.csv', header =T)

attach(TP_F)

TP_F = na.omit(TP_F)
TP_F$Date<-strptime(Date,format="%m/%d/%Y") #defining what is the original format of your date
TP_F$Date<-as.Date(TP_F$Date,format="%m-%d-%Y")

TP_F <- TP_F %>%
        filter(Date >= as.Date('2004-01-01') & Date <= as.Date('2018-12-31'))
attach(TP_F)
head(TP_F)
#TPplot <- ggplot(datavar, aes(x=loggeddischarge, y= loggedtemp))+geom_point()
TPplot <- ggplot(TP_F, aes(x= Q6, y= C6))+geom_point()
TPplot
# linear model
#linearModelVar <- lm(loggedtemp ~ loggeddischarge, datavar)
linearModelVar6 <- lm(C6 ~ Q6, TP_F)
#display linear model
linearModelVar6
summary(linearModelVar6)
# Davies test for significant breakpoint
#turbdavies <- davies.test(linearModelVar,seg.Z =~loggeddischarge,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
TPdavies <- davies.test(linearModelVar6,seg.Z =~Q6,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
TPdavies 
#########################

pscore.test(linearModelVar6, k = 10, alternative = c("two.sided", "less", "greater"),
            values=NULL, dispersion=NULL, df.t=NULL, more.break=FALSE)

TP.seg <- segmented(linearModelVar6, seg.Z = ~ Q6,it.max=1000)
#summary(tp.seg1)
summary.seg6 = summary(TP.seg)
summary.seg6

confint(TP.seg , 'Q6', level=0.95, rev.sgn=FALSE, var.diff=FALSE,
        digits=max(4, getOption("digits") - 1))

TP.seg$psi
#estimate bp which is already in the summary
TPestbp <-summary.segmented(TP.seg)$psi [1,2]
TPestbp

TPestderror <- summary.segmented(TP.seg)$psi [1,3]
slope(TP.seg)



my.fitted6 <- fitted(TP.seg)
#my.model <- data.frame(discharge=datavar$loggeddischarge, loggedturbidity=my.fitted)
my.model6 <- data.frame(Discharge=TP_F$Q6, C6=my.fitted6)

high.TP= subset(TP_F, Q6 >= TP.seg$psi[2])
low.TP <- subset(TP_F,Q6 < TP.seg$psi[2])

#anova

TPlowaov1 <-aov(low.TP$C6 ~ low.TP$Q6, data = low.TP)
summary(TPlowaov1)

TPhighaov1 <-aov(high.TP$C6 ~ high.TP$Q6, data = high.TP)
summary(TPhighaov1)

TPplot <- ggplot(TP_F,aes(x=Q6, y= C6))+ 
  geom_point( aes( x=Q6, y= C6), color= 'black') #shape = temppch)
TPplot


ggplot(my.model6, aes(x=Q6, y=C6)) + geom_line()
breakpointplot6=TPplot + geom_line(data = my.model6, aes(x = Q6, y = C6), colour = "red", size = 1.25)

TPmy.lines <- TP.seg$psi[, 2]
#tiff("TPplot1.tiff", width = 5, height =3, units = 'in', res = 600)
TPplot1 <- breakpointplot6+geom_vline(xintercept=TPmy.lines,linetype="dashed", col ="red", size= 1)+
  xlab(expression(Discharge~(m^3~s^-1)))+ylab(expression(TP~(mg~L^-1)))+
  theme(panel.border =  element_rect(color = "black", fill = NA, size= 1),
        panel.background=element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position="top")+
  theme(axis.text.x = element_text(color = "grey20", size = 12,  hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12,  hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 16,  hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 16,  hjust = .5, vjust = .5, face = "plain"))+
  #transfomrm scale  back to normal and round to two decimal places
  scale_x_continuous(breaks = c(-2, -1, 0, 1,2,3), labels =round(c(10^(-2),10^(-1), 10^(0),10^(1),10^(2),10^(3)), 3))+
    scale_y_continuous(breaks =c(-1, -0.5, 0, 0.5, 1), labels =round(c(10^(-1),10^(-0.5), 10^(0), 10^(0.5),10^(1)),1))
      #breaks=seq(0,100, by = 20)))
  #text(x, y, labels)
TPplot1  
#tiff("TPplot1.tiff", width = 4, height = 4, units = 'in', res = 600)
#plot(x, y) # Make plot
dev.off()

#####################################################################
SpC_F =read.csv("prb_spc_F.csv", header=T)
#TP_F =TP_F[!duplicated(TP_F),]

attach(SpC_F)
SpC_F$Date<-strptime(Date,format="%m/%d/%Y") #defining what is the original format of your date
SpC_F$Date<-as.Date(SpC_F$Date,format="%m-%d-%Y")

SpC_F <- SpC_F %>%
        filter(Date >= as.Date('2004-01-01') & Date <= as.Date('2018-12-31'))
attach(SpC_F)
head(SpC_F)
#SpCplot <- ggplot(datavar, aes(x=loggeddischarge, y= loggedtemp))+geom_point()
SpCplot <- ggplot(SpC_F, aes(x= Q9, y= C9))+geom_point()
SpCplot
# linear model
#linearModelVar <- lm(loggedtemp ~ loggeddischarge, datavar)
linearModelVar9 <- lm(C9 ~ Q9, SpC_F)
#display linear model
linearModelVar9
summary(linearModelVar9)
# Davies test for significant breakpoint
#turbdavies <- davies.test(linearModelVar,seg.Z =~loggeddischarge,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
SpCdavies <- davies.test(linearModelVar9,seg.Z =~Q9,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
SpCdavies 
#########################

pscore.test(linearModelVar9, k = 10, alternative = c("two.sided", "less", "greater"),
            values=NULL, dispersion=NULL, df.t=NULL, more.break=FALSE)

SpC.seg <- segmented(linearModelVar9, seg.Z = ~ Q9,it.max=1000)
#summary(SpC.seg1)
summary.seg9= summary(SpC.seg)
summary.seg9

SpC.seg$psi
#estimate bp which is already in the summary
SpCestbp <-summary.segmented(SpC.seg)$psi [1,2]
SpCestbp

confint(SpC.seg , 'Q9', level=0.95, rev.sgn=FALSE, var.diff=FALSE,
        digits=max(4, getOption("digits") - 1))

SpCestderror <- summary.segmented(SpC.seg)$psi [1,3]
slope(SpC.seg)



my.fitted9 <- fitted(SpC.seg)
#my.model <- data.frame(discharge=datavar$loggeddischarge, loggedturbidity=my.fitted)
my.model9 <- data.frame(Discharge=SpC_F$Q9, C9=my.fitted9)

high.SpC= subset(SpC_F, Q9 >= SpC.seg$psi[2])
low.SpC <- subset(SpC_F,Q9 < SpC.seg$psi[2])

#anova

SpClowaov1 <-aov(low.SpC$C9 ~ low.SpC$Q9, data = low.SpC)
summary(SpClowaov1)

SpChighaov1 <-aov(high.SpC$C9 ~ high.SpC$Q9, data = high.SpC)
summary(SpChighaov1)

SpCplot <- ggplot(SpC_F,aes(x=Q9, y= C9))+
  geom_point( aes( x=Q9, y= C9), color= 'black') #shape = temppch)
SpCplot


ggplot(my.model9, aes(x=Q9, y=C9)) + geom_line()
breakpoint9=SpCplot + geom_line(data = my.model9, aes(x = Q9, y = C9), colour = "red", size = 1.25)

SpCmy.lines <- SpC.seg$psi[, 2]
tiff("Sreview_SpCplot2.tiff", width = 5, height =3, units = 'in', res = 600)
SpCplot1 <- breakpoint9+geom_vline(xintercept=SpCmy.lines,linetype="dashed", col ="red", size= 1)+
  xlab(expression(Discharge~(m^3~s^-1)))+ylab(expression(SC~(uS~cm^-1)))+
  theme(panel.border =  element_rect(color = "black", fill = NA, size=1),
        panel.background=element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position="top")+
  theme(axis.text.x = element_text(color = "grey20", size = 12,  hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12,  hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 16,  hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 16,  hjust = .5, vjust = .5, face = "plain"))+
  #transfomrm scale  back to normal and round to two decimal places
  scale_x_continuous(breaks = c(-2, -1, 0, 1,2,3), labels =round(c(10^(-2), 10^(-1), 10^(0), 10^(1), 10^(2), 10^(3)),2))+
    scale_y_continuous(breaks = c( 2.39794, 2.69897), labels =round(c (10^(2.39794),10^(2.69897))))
                      
SpCplot1

#################################################################
turb_F =read.csv("prb_turb_F.csv", header=T)
#TP_F =TP_F[!duplicated(TP_F),]
attach(turb_F)
  
#turb_F = na.omit(turb_F)

turb_F$Date<-strptime(Date,format="%m/%d/%Y") #defining what is the original format of your date
turb_F$Date<-as.Date(turb_F$Date,format="%m-%d-%Y")

turb_F <- turb_F %>%
        filter(Date >= as.Date('2004-01-01') & Date <= as.Date('2018-12-31'))
attach(turb_F)
head(turb_F)

#turb_F = read.csv('prb_turb_F.csv', header =T)

#turbplot <- ggplot(datavar, aes(x=loggeddischarge, y= loggedtemp))+geom_point()
turbplot <- ggplot(turb_F, aes(x= Q8, y= C8))+geom_point()
turbplot
# linear model
#linearModelVar <- lm(loggedtemp ~ loggeddischarge, datavar)

linearModelVar8 <- lm(C8 ~ Q8, turb_F)
#display linear model
summary(linearModelVar8)

# Davies test for significant breakpoint
#turbdavies <- davies.test(linearModelVar,seg.Z =~loggeddischarge,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
turbdavies <- davies.test(linearModelVar8,seg.Z =~Q8,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
turbdavies 
#########################

pscore.test(linearModelVar8, k = 10, alternative = c("two.sided", "less", "greater"),
            values=NULL, dispersion=NULL, df.t=NULL, more.break=FALSE)

turb.seg1 <- segmented(linearModelVar8, seg.Z = ~ Q8,it.max=1000)
#summary(tp.seg1)
summary.seg.turb = summary(turb.seg1)
summary.seg.turb

confint(turb.seg1, 'Q8', level=0.95, rev.sgn=FALSE, var.diff=FALSE,
        digits=max(4, getOption("digits") - 1))
turb.seg1$psi
#estimate bp which is already in the summary
turbestbp1 <-summary.segmented(turb.seg1)$psi [1,2]
turbestbp1

turbestderror1 <- summary.segmented(turb.seg1)$psi [1,3]
slope(turb.seg1)




my.fitted8 <- fitted(turb.seg1)
#my.model <- data.frame(discharge=datavar$loggeddischarge, loggedturbidity=my.fitted)
my.model8 <- data.frame(Discharge=turb_F$Q8, C8=my.fitted8)

high.turb= subset(turb_F, Q8 >= turb.seg1$psi[2])
low.turb <- subset(turb_F,Q8 < turb.seg1$psi[2])

#anova

turblowaov <-aov(low.turb$C8 ~ low.turb$Q8, data = low.turb)
summary(turblowaov)

turbhighaov <-aov(high.turb$C8 ~ high.turb$Q8, data = high.turb)
summary(turbhighaov)

turbplot <- ggplot(turb_F,aes(Station, x=Q8, y= C8))+
  geom_point(aes( x=Q8, y= C8), color= 'black') #shape = temppch)
turbplot


ggplot(my.model8, aes(x=Q8, y=C8)) + geom_line()
breakpointplot8=turbplot + geom_line(data = my.model8, aes(x = Q8, y = C8), colour = "red", size = 1.25)

turbmy.lines <- turb.seg1$psi[, 2]



tiff(" reviewturbplot1.tiff", width = 5, height =3, units = 'in', res = 600)
turbplot1 <- breakpointplot8+geom_vline(xintercept=turbmy.lines,linetype="dashed", col ="red", size= 1)+
  xlab(expression(Discharge~(m^3~s^-1)))+ylab(expression(Turbidity~(NTU)))+
  theme(panel.border =  element_rect(color = "black", fill = NA, size=1),
        panel.background=element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position="top")+
  theme(axis.text.x = element_text(color = "grey20", size = 12,  hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12,  hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 16,  hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 16,  hjust = .5, vjust = .5, face = "plain"))+
        #axis.text.x     = element_text(size = 8)
  #transfomrm scale  back to normal and round to two decimal places
  scale_x_continuous(breaks = c(-2, -1, 0, 1,2,3), labels =round(c(10^(-2),10^(-1), 10^(0),10^(1),10^(2),10^(3)), 3))+
    scale_y_discrete(limits = c(0, 1.0, 2), labels =round(c(10^(0), 10^(1.0), 10^(2))))
    
  #scale_y_continuous(breaks = c(0, 1, 1.5, 2), labels =round(c(10^(0), 10^(1), 10^(1.5), 10^(2)),2))                    
turbplot1
dev.off()


################### Hillsboro Canal ##################################
S6_TP = read.csv("S6_final_TP.csv", header =T)
attach(S6_TP)
S6_TP$date<-strptime(date,format="%m/%d/%Y")#defining what is the original format of your date
S6_TP$date<-as.Date(S6_TP$date,format="%Y-%m-%d")
S6_flow = read.csv("flowwithaveecolumnadded.csv", header =T)
attach(S6_flow)
#s6_flow =flowwithaveecolumnadded

head(S6_flow)
S6_flow$date<-strptime(date,format="%m/%d/%Y")
S6_flow$date<-as.Date(S6_flow$date,format="%Y-%m-%d")

S6_TP_combined = merge(S6_flow, S6_TP, by ="date")
#S6_TP_combined= rename(S6_TP_combined, Flow = "S6_P_FLOW_cfs" )
 
#S6_TP_combined = merge(S6_flow, S6_TP, by ="date")
head(S6_TP_combined)

TP_F= S6_TP_combined
TP_F= S6_TP_combined
TP_F= mutate(TP_F,
  Discharge = Flow*0.0283 ,
  
)



#log transformation 

TP_F <- TP_F[TP_F$Discharge > 0, ]
TP_F <- TP_F[TP_F$TP > 0, ]
TP_F= mutate(TP_F,
  Q6 = log10(Discharge) ,
  C6 = log10(TP)

)
TP_F = na.omit(TP_F)

attach (TP_F)
head(TP_F)

#Q6
TPplot <- ggplot(TP_F, aes(x= Q6, y= C6))+geom_point()
TPplot
# linear model
#linearModelVar <- lm(loggedtemp ~ loggeddischarge, datavar)
linearModelVar6 <- lm(C6 ~ Q6, TP_F)
#display linear model
linearModelVar6
summary(linearModelVar6)
# Davies test for significant breakpoint
#turbdavies <- davies.test(linearModelVar,seg.Z =~loggeddischarge,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
TPdavies <- davies.test(linearModelVar6,seg.Z =~Q6,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
TPdavies 
#########################

pscore.test(linearModelVar6, k = 10, alternative = c("two.sided", "less", "greater"),
            values=NULL, dispersion=NULL, df.t=NULL, more.break=FALSE)

TP.seg <- segmented(linearModelVar6, seg.Z = ~ Q6,it.max=1000)

#summary(tp.seg1)
summary.seg6 = summary(TP.seg)
summary.seg6

TP.seg$psi
#estimate bp which is already in the summary
TPestbp <-summary.segmented(TP.seg)$psi [1,2]
TPestbp

#confindence interval 95%
confint(TP.seg)
confint(TP.seg, 'Q6', level=0.95, rev.sgn=FALSE, var.diff=FALSE,
        digits=max(4, getOption("digits") - 1))

TPestderror <- summary.segmented(TP.seg)$psi [1,3]
slope(TP.seg)



my.fitted6 <- fitted(TP.seg)
#my.model <- data.frame(discharge=datavar$loggeddischarge, loggedturbidity=my.fitted)
my.model6 <- data.frame(Discharge=TP_F$Q6, C6=my.fitted6)

high.TP= subset(TP_F, Q6 >= TP.seg$psi[2])
low.TP <- subset(TP_F,Q6 < TP.seg$psi[2])

#anova

TPlowaov1 <-aov(low.TP$C6 ~ low.TP$Q6, data = low.TP)
summary(TPlowaov1)

TPhighaov1 <-aov(high.TP$C6 ~ high.TP$Q6, data = high.TP)
summary(TPhighaov1)

TPplot <- ggplot(TP_F,aes(x=Q6, y= C6))+
  geom_point( aes( x=Q6, y= C6), color= 'black') #shape = temppch)
TPplot



ggplot(my.model6, aes(x=Q6, y=C6)) + geom_line()
breakpointplot6=TPplot + geom_line(data = my.model6, aes(x = Q6, y = C6), colour = "red", size = 1.25)

TPmy.lines <- TP.seg$psi[, 2]

tiff("review_TPplot1_manu.tiff", width = 5, height =3, units = 'in', res = 600) #600dpi
TPplot1 <- breakpointplot6+geom_vline(xintercept=TPmy.lines,linetype="dashed", col ="red", size= 1)+
  xlab(expression(Discharge~(m^3~s^-1)))+ylab(expression(TP~(mg~L^-1)))+
  theme(panel.border =  element_rect(color = "black", fill = NA, size= 1),
        panel.background=element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position="top")+
  theme(axis.text.x = element_text(color = "grey20", size = 8,  hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 8,  hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 14,  hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 14,  hjust = .5, vjust = .5, face = "plain"))+
    scale_x_continuous(breaks = c(-3,-2, -1, 0, 1,2,3), labels =round(c(10^(-3),10^(-2),10^(-1), 10^(0),10^(1),10^(2),10^(3)), 3))+
       scale_y_discrete(limits=c(-2,-1,0,1), labels =round(c(10^(-2),10^(-1),10^(0), 10^(1)),2)) 
 
TPplot1 

NNplot <- ggplot(NN_F, aes(x= Q1, y= C1))+geom_point()
NNplot
# linear model
#linearModelVar <- lm(loggedtemp ~ loggeddischarge, datavar)

linearModelVar1 <- lm(C1 ~ Q1, NN_F)
#display linear model
summary(linearModelVar1)

# Davies test for significant breakpoint
#turbdavies <- davies.test(linearModelVar,seg.Z =~loggeddischarge,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
NNdavies <- davies.test(linearModelVar1,seg.Z =~Q1,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
NNdavies 
##################################################################

pscore.test(linearModelVar1, k = 10, alternative = c("two.sided", "less", "greater"),
            values=NULL, dispersion=NULL, df.t=NULL, more.break=FALSE)

nn.seg1 <- segmented(linearModelVar1, seg.Z = ~ Q1,it.max=1000)
#summary(tp.seg1)
summary.seg.nn = summary(nn.seg1)
summary.seg.nn

confint(nn.seg1, 'Q1', level=0.95, rev.sgn=FALSE, var.diff=FALSE,
        digits=max(4, getOption("digits") - 1))
nn.seg1$psi
#estimate bp which is already in the summary
nnestbp1 <-summary.segmented(nn.seg1)$psi [1,2]
nnestbp1

nnestderror1 <- summary.segmented(nn.seg1)$psi [1,3]
slope(nn.seg1)


my.fitted2 <- fitted(nn.seg1)
#my.model <- data.frame(discharge=datavar$loggeddischarge, loggedturbidity=my.fitted)
my.model2 <- data.frame(Discharge=NN_F$Q1, C1=my.fitted2)

high.nn= subset(NN_F, Q1 >= nn.seg1$psi[2])
low.nn <- subset(NN_F,Q1 < nn.seg1$psi[2])

#anova

nnlowaov <-aov(low.nn$C1 ~ low.nn$Q1, data = low.nn)
summary(nnlowaov)

nnhighaov <-aov(high.nn$C1 ~ high.nn$Q1, data = high.nn)
summary(nnhighaov)

NNplot <- ggplot(NN_F,aes(Station, x=Q1, y= C1))+
  geom_point(aes( x=Q1, y= C1), color= 'black') #shape = temppch)
NNplot


ggplot(my.model2, aes(x=Q1, y=C1)) + geom_line()
breakpointplot2=NNplot + geom_line(data = my.model2, aes(x = Q1, y = C1), colour = "red", size = 1.25)

nnmy.lines <- nn.seg1$psi[, 2]


#tiff("NNplot1yes.tiff", width = 5, height =3, units = 'in', res = 600)

#tiff("NNplot_manu.tiff", width = 5, height =3, units = 'in', res = 600) #600dpi
tiff("review_nn_final.tiff", width = 5, height =3, units = 'in', res = 600)
nnplot1 <- breakpointplot2+geom_vline(xintercept=nnmy.lines,linetype="dashed", col ="red", size= 1)+
  xlab(expression(Discharge~(m^3~s^-1)))+ylab(expression(NN~(mg~L^-1)))+
  theme(panel.border =  element_rect(color = "black", fill = NA, size= 1),
        panel.background=element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position="top")+
  theme(axis.text.x = element_text(color = "grey20", size = 8,  hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 8,  hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 14,  hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 14,  hjust = .5, vjust = .5, face = "plain"))+
   scale_x_continuous(breaks = c(-1,0, 1,2 ), labels =round(c(10^(-1),10^(0),10^(1),10^(2)),3))+
    scale_y_continuous(breaks =c(-2, -1, 0,1), labels =round(c(10^(-2), 10^(-1), 10^(0), 10^(1)),2))
  
nnplot1

########################################################
S6_turb = read.csv("s6_turb.csv", header =T)
attach(S6_turb)
S6_turb$date<-strptime(date,format="%m/%d/%Y")#defining what is the original format of your date
S6_turb$date<-as.Date(S6_turb$date,format="%Y-%m-%d") #defining what is the desired format of your date

head(S6_flow)
S6_turb_combined = merge(S6_flow, S6_turb, by ="date")
#S6_turb_combined= rename(S6_turb_combined, Flow = "S6_P_FLOW_cfs" )


#S6_turb_combined = merge(S6_flow, S6_turb, by ="date")
head(S6_turb_combined)

turb_F= S6_turb_combined
turb_F= S6_turb_combined
turb_F= mutate(turb_F,
  Discharge = Flow*0.0283 ,
  
)
head(turb_F)


turb_F <- turb_F[turb_F$Discharge > 0, ]
turb_F <- turb_F[turb_F$Turb > 0, ]
turb_F= mutate(turb_F,
  Q8 = log10(Discharge) ,
  C8 = log10(Turb)

)
turb_F = na.omit(turb_F)
attach (turb_F)
head(turb_F)
turbplot <- ggplot(turb_F, aes(x= Q8, y= C8))+geom_point()
turbplot
# linear model
#linearModelVar <- lm(loggedtemp ~ loggeddischarge, datavar)

linearModelVar8 <- lm(C8 ~ Q8, turb_F)
#display linear model
summary(linearModelVar8)

# Davies test for significant breakpoint
#turbdavies <- davies.test(linearModelVar,seg.Z =~loggeddischarge,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
turbdavies <- davies.test(linearModelVar8,seg.Z =~Q8,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
turbdavies 
#########################

pscore.test(linearModelVar8, k = 10, alternative = c("two.sided", "less", "greater"),
            values=NULL, dispersion=NULL, df.t=NULL, more.break=FALSE)

turb.seg1 <- segmented(linearModelVar8, seg.Z = ~ Q8,it.max=1000)
#summary(tp.seg1)
summary.seg.turb = summary(turb.seg1)
summary.seg.turb

confint(turb.seg1, 'Q8', level=0.95, rev.sgn=FALSE, var.diff=FALSE,
        digits=max(4, getOption("digits") - 1))
turb.seg1$psi
#estimate bp which is already in the summary
turbestbp1 <-summary.segmented(turb.seg1)$psi [1,2]
turbestbp1

turbestderror1 <- summary.segmented(turb.seg1)$psi [1,3]
slope(turb.seg1)




my.fitted8 <- fitted(turb.seg1)
#my.model <- data.frame(discharge=datavar$loggeddischarge, loggedturbidity=my.fitted)
my.model8 <- data.frame(Discharge=turb_F$Q8, C8=my.fitted8)

high.turb= subset(turb_F, Q8 >= turb.seg1$psi[2])
low.turb <- subset(turb_F,Q8 < turb.seg1$psi[2])

#anova

turblowaov <-aov(low.turb$C8 ~ low.turb$Q8, data = low.turb)
summary(turblowaov)

turbhighaov <-aov(high.turb$C8 ~ high.turb$Q8, data = high.turb)
summary(turbhighaov)

turbplot <- ggplot(turb_F,aes(Station, x=Q8, y= C8))+
  geom_point(aes( x=Q8, y= C8), color= 'black') #shape = temppch)
turbplot


ggplot(my.model8, aes(x=Q8, y=C8)) + geom_line()
breakpointplot8=turbplot + geom_line(data = my.model8, aes(x = Q8, y = C8), colour = "red", size = 1.25)

turbmy.lines <- turb.seg1$psi[, 2]



tiff("reviewturbplot1.tiff", width = 5, height =3, units = 'in', res = 600)
turbplot1 <- breakpointplot8+geom_vline(xintercept=turbmy.lines,linetype="dashed", col ="red", size= 1)+
  xlab(expression(Discharge~(m^3~s^-1)))+ylab(expression(Turbidity~(NTU)))+
  theme(panel.border =  element_rect(color = "black", fill = NA, size= 1),
        panel.background=element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position="top")+
  theme(axis.text.x = element_text(color = "grey20", size = 8,  hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 8,  hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 14,  hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 14,  hjust = .5, vjust = .5, face = "plain"))+
   
#require(scales)
#turbplot1  + scale_x_continuous(labels = comma)
scale_x_continuous(breaks = c(-3,-2, -1, 0, 1,2,3), labels =round(c(10^(-3),10^(-2),10^(-1), 10^(0),10^(1),10^(2),10^(3)), 3))+
       scale_y_discrete(limits = c(0, 1, 2), labels =round(c(10^(0),  10^(1), 10^(2)),1))
 
turbplot1

######################
S6_Cl = read.csv("S6_cl.csv", header =T)
attach(S6_Cl)
S6_Cl$date<-strptime(date,format="%m/%d/%Y")#defining what is the original format of your date
S6_Cl$date<-as.Date(S6_Cl$date,format="%Y-%m-%d") #defining what is the desired format of your date
S6_Cl_combined = merge(S6_flow, S6_Cl, by ="date")
head(S6_Cl_combined)

Cl_F= S6_Cl_combined
Cl_F= S6_Cl_combined
Cl_F= mutate(Cl_F,
  Discharge = Flow*0.0283 ,
  
)
head(Cl_F)
Cl_F <- Cl_F[Cl_F$Discharge > 0, ]
Cl_F <- Cl_F[Cl_F$Cl > 0, ]
Cl_F= mutate(Cl_F,
  Q6 = log10(Discharge) ,
  C6 = log10(Cl)

)
Cl_F = na.omit(Cl_F)
attach (Cl_F)
head(Cl_F)


```
```{r}
Clplot <- ggplot(Cl_F, aes(x= Q6, y= C6))+geom_point()
Clplot
# linear model
#linearModelVar <- lm(loggedtemp ~ loggeddischarge, datavar)
linearModelVar6 <- lm(C6 ~ Q6, Cl_F)
#display linear model
linearModelVar6
summary(linearModelVar6)
# Davies test for significant breakpoint
#turbdavies <- davies.test(linearModelVar,seg.Z =~loggeddischarge,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
Cldavies <- davies.test(linearModelVar6,seg.Z =~Q6,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
Cldavies 
#########################

pscore.test(linearModelVar6, k = 10, alternative = c("two.sided", "less", "greater"),
            values=NULL, dispersion=NULL, df.t=NULL, more.break=FALSE)

Cl.seg <- segmented(linearModelVar6, seg.Z = ~ Q6,it.max=1000)

#summary(Cl.seg1)
summary.seg6 = summary(Cl.seg)
summary.seg6

Cl.seg$psi
#estimate bp which is already in the summary
Clestbp <-summary.segmented(Cl.seg)$psi [1,2]
Clestbp

#confindence interval 95%
confint(Cl.seg)
confint(Cl.seg, 'Q6', level=0.95, rev.sgn=FALSE, var.diff=FALSE,
        digits=max(4, getOption("digits") - 1))

Clestderror <- summary.segmented(Cl.seg)$psi [1,3]
slope(Cl.seg)



my.fitted6 <- fitted(Cl.seg)
#my.model <- data.frame(discharge=datavar$loggeddischarge, loggedturbidity=my.fitted)
my.model6 <- data.frame(Discharge=Cl_F$Q6, C6=my.fitted6)

high.Cl= subset(Cl_F, Q6 >= Cl.seg$psi[2])
low.Cl <- subset(Cl_F,Q6 < Cl.seg$psi[2])

#anova

Cllowaov1 <-aov(low.Cl$C6 ~ low.Cl$Q6, data = low.Cl)
summary(Cllowaov1)

Clhighaov1 <-aov(high.Cl$C6 ~ high.Cl$Q6, data = high.Cl)
summary(Clhighaov1)

Clplot <- ggplot(Cl_F,aes(x=Q6, y= C6))+
  geom_point( aes( x=Q6, y= C6), color= 'black') #shape = temppch)
Clplot



ggplot(my.model6, aes(x=Q6, y=C6)) + geom_line()
breakpoinCllot6=Clplot + geom_line(data = my.model6, aes(x = Q6, y = C6), colour = "red", size = 1.25)

Clmy.lines <- Cl.seg$psi[, 2]

#tiff("Clplot1.tiff", width = 5, height =3, units = 'in', res = 600)
Clplot1 <- breakpoinCllot6+geom_vline(xintercept=Clmy.lines,linetype="dashed", col ="red", size= 1)+
  xlab(expression(Discharge~(m^3~s^-1)))+ylab(expression(Cl~(mgL^-1)))+
  theme(panel.border =  element_rect(color = "black", fill = NA, size= 1),
        panel.background=element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position="top")+
  theme(axis.text.x = element_text(color = "grey20", size = 8,  hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 8,  hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 16,  hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 16,  hjust = .5, vjust = .5, face = "plain"))+
   scale_x_continuous(breaks = c(-2,-1, 0, 1,2,3), labels =round(c(10^(-2),10^(-1), 10^(0), 10^(1), 10^(2), 10^(3)),2))+
    scale_y_discrete(limits = c(0,1, 2, 3), labels =round(c(10^(0), 10^(1), 10^(2), 10^(3)),1))
Clplot1 
#scale_y_discrete(limits = c(0, 1, 2), labels =round(c(10^(0),  10^(1), 10^(2)),1))
#t6 = (mean(Discharge)/mean(Cl))* (sd(Cl)/sd(Discharge))
 
#t = CVc/CVq
t6
###################################
S6_SpC = read.csv("s6_final_spc.csv", header =T)
attach(S6_SpC)
S6_SpC$date<-strptime(date,format="%m/%d/%Y")#defining what is the original format of your date
S6_SpC$date<-as.Date(S6_SpC$date,format="%Y-%m-%d") #defining what is the desired format of your date
head(S6_flow)
S6_SpC_combined = merge(S6_flow, S6_SpC, by ="date")
head(S6_SpC_combined)

SpC_F= S6_SpC_combined
SpC_F= S6_SpC_combined
SpC_F= mutate(SpC_F,
  Discharge = Flow*0.0283 ,
  
)

SpC_F <- SpC_F[SpC_F$Discharge > 0, ]
SpC_F <- SpC_F[SpC_F$SpC > 0, ]
SpC_F= mutate(SpC_F,
  Q9 = log10(Discharge) ,
  C9 = log10(SpC)

)
SpC_F = na.omit(SpC_F)
attach (SpC_F)
head(SpC_F)
attach(SpC_F)
SpCplot <- ggplot(SpC_F, aes(x= Q9, y= C9))+geom_point()
SpCplot
# linear model
#linearModelVar <- lm(loggedtemp ~ loggeddischarge, datavar)
linearModelVar9 <- lm(C9 ~ Q9, SpC_F)
#display linear model
linearModelVar9
summary(linearModelVar9)
# Davies test for significant breakpoint
#turbdavies <- davies.test(linearModelVar,seg.Z =~loggeddischarge,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
SpCdavies <- davies.test(linearModelVar9,seg.Z =~Q9,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
SpCdavies 
#########################

pscore.test(linearModelVar9, k = 10, alternative = c("two.sided", "less", "greater"),
            values=NULL, dispersion=NULL, df.t=NULL, more.break=FALSE)

SpC.seg <- segmented(linearModelVar9, seg.Z = ~ Q9,it.max=1000)
#summary(SpC.seg1)
summary.seg9= summary(SpC.seg)
summary.seg9

SpC.seg$psi
#estimate bp which is already in the summary
SpCestbp <-summary.segmented(SpC.seg)$psi [1,2]
SpCestbp

confint(SpC.seg , 'Q9', level=0.95, rev.sgn=FALSE, var.diff=FALSE,
        digits=max(4, getOption("digits") - 1))

SpCestderror <- summary.segmented(SpC.seg)$psi [1,3]
slope(SpC.seg)



my.fitted9 <- fitted(SpC.seg)
#my.model <- data.frame(discharge=datavar$loggeddischarge, loggedturbidity=my.fitted)
my.model9 <- data.frame(Discharge=SpC_F$Q9, C9=my.fitted9)

high.SpC= subset(SpC_F, Q9 >= SpC.seg$psi[2])
low.SpC <- subset(SpC_F,Q9 < SpC.seg$psi[2])

#anova

SpClowaov1 <-aov(low.SpC$C9 ~ low.SpC$Q9, data = low.SpC)
summary(SpClowaov1)

SpChighaov1 <-aov(high.SpC$C9 ~ high.SpC$Q9, data = high.SpC)
summary(SpChighaov1)

SpCplot <- ggplot(SpC_F,aes(x=Q9, y= C9))+
  geom_point( aes( x=Q9, y= C9), color= 'black') #shape = temppch)
SpCplot


ggplot(my.model9, aes(x=Q9, y=C9)) + geom_line()
breakpoint9=SpCplot + geom_line(data = my.model9, aes(x = Q9, y = C9), colour = "red", size = 1.25)

SpCmy.lines <- SpC.seg$psi[, 2]
tiff("review_SpCplot1.tiff", width = 5, height =3, units = 'in', res = 600)
SpCplot1 <- breakpoint9+geom_vline(xintercept=SpCmy.lines,linetype="dashed", col ="red", size= 1)+
  xlab(expression(Discharge~(m^3~s^-1)))+ylab(expression(SC~(uS~cm^-1)))+
  theme(panel.border =  element_rect(color = "black", fill = NA, size= 1),
        panel.background=element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position="top")+
  theme(axis.text.x = element_text(color = "grey20", size = 8,  hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 8,  hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 14,  hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 14,  hjust = .5, vjust = .5, face = "plain"))+
  #transfomrm scale  back to normal and round to two decimal places
  scale_x_continuous(breaks = c(-3, -2, -1, 0, 1,2,3), labels =round(c(10^(-3), 10^(-2), 10^(-1), 10^(0), 10^(1), 10^(2), 10^(3)),2))+
  scale_y_continuous(breaks = c( 2.69897,3,3.30103), labels =round(c(10^(2.69897),10^(3), 10^(3.30103))))  
  #scale_y_discrete(limits = c(2.75,3, 3.25), labels =round(c(10^(2.75),10^(3),10^(3.25)),0))
#(10^(2.5),10^(2.75),10^(3), 10^(3.25)
#scale_y_discrete(limits = c(0,1, 2, 3), labels =round(c(10^(0), 10^(1), 10^(2), 10^(3)),1))
                      
SpCplot1

t6 = (mean(Discharge)/mean(SpC))* (sd(SpC)/sd(Discharge))
 
#t = CVc/CVq
t6

S6_TSS = read.csv("s6_final_tss.csv", header =T)
attach(S6_TSS)
S6_TSS$date<-strptime(date,format="%m/%d/%Y")#defining what is the original format of your date
S6_TSS$date<-as.Date(S6_TSS$date,format="%Y-%m-%d") #defining what is the desired format of your date
head(S6_flow)
S6_TSS_combined = merge(S6_flow, S6_TSS, by ="date")
head(S6_TSS_combined)

TSS_F= S6_TSS_combined
TSS_F= S6_TSS_combined
TSS_F= mutate(TSS_F,
  Discharge = Flowbyav*0.0283 ,
  
)

TSS_F <- TSS_F[TSS_F$Discharge > 0, ]
TSS_F <- TSS_F[TSS_F$TSS > 0, ]
TSS_F= mutate(TSS_F,
  Q6 = log10(Discharge) ,
  C6 = log10(TSS)

)
TSS_F = na.omit(TSS_F)
attach (TSS_F)
head(TSS_F)
```
```{r}
TSSplot <- ggplot(TSS_F, aes(x= Q6, y= C6))+geom_point()
TSSplot
# linear model
#linearModelVar <- lm(loggedtemp ~ loggeddischarge, datavar)
linearModelVar6 <- lm(C6 ~ Q6, TSS_F)
#display linear model
linearModelVar6
summary(linearModelVar6)
# Davies test for significant breakpoint
#TSSdavies <- davies.test(linearModelVar,seg.Z =~loggeddischarge,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
TSSdavies <- davies.test(linearModelVar6,seg.Z =~Q6,k=10,alternative=c("two.sided","less","greater"), values=NULL,dispersion=NULL)
TSSdavies 
#########################

pscore.test(linearModelVar6, k = 10, alternative = c("two.sided", "less", "greater"),
            values=NULL, dispersion=NULL, df.t=NULL, more.break=FALSE)

TSS.seg <- segmented(linearModelVar6, seg.Z = ~ Q6,it.max=1000)

#summary(TSS.seg1)
summary.seg6 = summary(TSS.seg)
summary.seg6

TSS.seg$psi
#estimate bp which is already in the summary
TSSestbp <-summary.segmented(TSS.seg)$psi [1,2]
TSSestbp

#confindence interval 95%
confint(TSS.seg)
confint(TSS.seg, 'Q6', level=0.95, rev.sgn=FALSE, var.diff=FALSE,
        digits=max(4, getOption("digits") - 1))

TSSestderror <- summary.segmented(TSS.seg)$psi [1,3]
slope(TSS.seg)



my.fitted6 <- fitted(TSS.seg)
#my.model <- data.frame(discharge=datavar$loggeddischarge, loggedTSSidity=my.fitted)
my.model6 <- data.frame(Discharge=TSS_F$Q6, C6=my.fitted6)

high.TSS= subset(TSS_F, Q6 >= TSS.seg$psi[2])
low.TSS <- subset(TSS_F,Q6 < TSS.seg$psi[2])

#anova

TSSlowaov1 <-aov(low.TSS$C6 ~ low.TSS$Q6, data = low.TSS)
summary(TSSlowaov1)

TSShighaov1 <-aov(high.TSS$C6 ~ high.TSS$Q6, data = high.TSS)
summary(TSShighaov1)

TSSplot <- ggplot(TSS_F,aes(x=Q6, y= C6))+
  geom_point( aes( x=Q6, y= C6), color= 'black') #shape = temppch)
TSSplot

    

ggplot(my.model6, aes(x=Q6, y=C6)) + geom_line()
breakpoinTSSlot6=TSSplot + geom_line(data = my.model6, aes(x = Q6, y = C6), colour = "red", size = 1.25)

TSSmy.lines <- TSS.seg$psi[, 2]

#tiff("new_TSSplot1.tiff", width = 5, height =3, units = 'in', res = 600)
TSSplot1 <- breakpoinTSSlot6+geom_vline(xintercept=TSSmy.lines,linetype="dashed", col ="red", size= 1)+
  xlab(expression(Discharge~(m^3~s^-1)))+ylab(expression(TSS~(mg~L^-1)))+
  theme(panel.border =  element_rect(color = "black", fill = NA, size= 1),
        panel.background=element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position="top")+
  theme(axis.text.x = element_text(color = "grey20", size = 8,  hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 8,  hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 16,  hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 16,  hjust = .5, vjust = .5, face = "plain"))+
   scale_x_continuous(breaks = c(-3,-2,-1.5, 0, 1,2), labels =round(c(10^(-3), 10^(-2),10^(-1.5), 10^(0), 10^(1), 10^(2)),2))+
    scale_y_continuous(breaks = c(0.5,1, 1.5,2), labels =round(c(10^(0.5), 10^(1), 10^(1.5), 10^(2)),2))
TSSplot1 

t6 = (mean(Discharge)/mean(TSS))* (sd(TSS)/sd(Discharge))
 
#t = CVc/CVq
t6

#################
```

